---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
options(repos = c(RSPM = "https://packagemanager.posit.co/cran/latest",
				  CRAN = "https://cloud.r-project.org/"),
		install.packages.check.source = "no",
		pkgType = "mac.binary")
```

# SuperSelector

<!-- badges: start -->
[![R-CMD-check](https://github.com/saraemoore/SuperSelector/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/saraemoore/SuperSelector/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

The `SuperSelector` package extends Cross-Validated [SuperLearner](https://github.com/ecpolley/SuperLearner) (`SuperLearner::CV.SuperLearner()`) for ensembled feature selection. This package also contains utility functions for simulating input data for, and visualizing outputs from, its feature selection algorithm.

## Installation

The SuperSelector package is currently only available via GitHub. To install:

```{r install_pkg, results='hide'}
remotes::install_github("saraemoore/SuperSelector")
```

## Examples

### Simple

From `?sim_toy_data`:

> Simulate data for a 3 continuous covariate, 1 binary outcome example where the outcome (Y) is unrelated to the first covariate (normally-distributed W1) but is related to the second and third covariates (lognormally-distributed W2 and W3, which are also related to one another).

```{r simple_example}
library(SuperSelector)
library(SuperLearner)  # for SL.mean, method.NNloglik
library(FSelector)     # for cutoff.biggest.diff

dat <- sim_toy_data(n_obs = 1000, rnd_seed = 54321)
res <- cvSLFeatureSelector(dat$Y,
						   dat[,-which(colnames(dat) %in% c("ID", "Y"))],
                           family = binomial())
```

```{r simple_example_table, results='asis'}
knitr::kable(res$whichVariable[,"keep_names", drop = FALSE])
```

```{r simple_example_plot1}
res_sum <- summarizeScreen(res$summary,
                           groupCols = "method")
p1 <- cvSLVarImpPlot(res_sum)
p1
```

```{r simple_example_plot2}
res_sum2 <- summarizeScreen(res$summary,
						    groupCols = c("method", "screener"))
p2 <- cvSLVarImpPlot2(res_sum2)
p2
```

### Advanced

From `?sim_proppr_data`:

> Simulate data for a 9 covariate, 1 binary outcome example where the outcome (Y) is unrelated to the first four covariates (normally-distributed W1:4) but is related to the remaining five covariates (some of which are also related to one another).

```{r advanced_example}
library(SuperSelector)
library(SuperLearner)  # for SL.mean, SL.glm, method.NNloglik
library(FSelector)     # for cutoff.biggest.diff, cutoff.k
# remotes::install_github("saraemoore/SLScreenExtra")
library(SLScreenExtra) # for screen.wgtd.lasso, screen.randomForest.imp, screen.earth.backwardprune

dat <- sim_proppr_data(n_obs = 500, rnd_seed = 54321)
dat_x <- dplyr::bind_cols(dat[, -which(colnames(dat) %in% c("GCS", "ID", "Y"))],
                          factor_to_indicator("GCS", dat))

libraryCVSLFeatSel <- list(
    `lasso mean` = c("SL.mean", "screen.wgtd.lasso"),
    `random forest biggest diff mean` = c("SL.mean", "screen.randomForest.imp"),
    `splines biggest diff mean` = c("SL.mean", "screen.earth.backwardprune"),
    `lasso glm` = c("SL.glm", "screen.wgtd.lasso"),
    `random forest biggest diff glm` = c("SL.glm", "screen.randomForest.imp"),
    `splines biggest diff glm` = c("SL.glm", "screen.earth.backwardprune")
)

libraryMetaFeatSel <- data.frame(selector = c("cutoff.biggest.diff", "cutoff.k", "cutoff.k"),
								k = c(NA, 3, 6),
								stringsAsFactors = FALSE)
rownames(libraryMetaFeatSel) <- c("biggest diff", "top3", "top6")

res <- cvSLFeatureSelector(as.numeric(dat$Y),
						   dat_x,
						   family = binomial(),
						   SL.library = libraryCVSLFeatSel,
						   selector.library = libraryMetaFeatSel,
						   nFolds = 5)
```

```{r advanced_example_table, results='asis'}
knitr::kable(res$whichVariable[,"keep_names", drop = FALSE])
```

```{r advanced_example_plot1}
res_sum <- summarizeScreen(res$summary,
                           groupCols = "method")
p1 <- cvSLVarImpPlot(res_sum)
p1
```

```{r advanced_example_plot2, fig.height=6}
res_sum2 <- summarizeScreen(res$summary,
						    groupCols = c("method", "screener"))
p2 <- cvSLVarImpPlot2(res_sum2)
p2
```
